COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2020-04-15 main.tex
Add additional semimajor axis panels to fig 6
Add libration width and surface density figure

\begin{figure*}
    \includegraphics[width=0.4\textwidth]{figures/coll_hist_e_and_m.png}
    \caption{Caption goes here.\label{fig:coll_hist_e_and_m}}
\end{figure*}

>>>>

\begin{figure*}
    \includegraphics[width=\textwidth]{figures/coll_hist_e_and_m.png}
    \caption{Caption goes here.\label{fig:coll_hist_e_and_m}}
\end{figure*}

\begin{figure*}
    \begin{center}
    \includegraphics[width=0.4\textwidth]{figures/e_and_m_surf_den.png}
    \caption{Caption goes here.\label{fig:e_and_m_surf_den}}
    \end{center}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures/lib_width.png}
    \caption{Caption goes here.\label{fig:lib_width}}
\end{figure*}
